Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-31 paper.qmd
Added fitted values scratch

<!-- The prediction approach involves performing the K-nearest neighbors (KNN) algorithm for an unsupervised classification problem. First, the nearest \pD{} model point is identified for a given new \pD{} point. Then, the corresponding \kD{} centroid mapping for the identified \pD{} model point is determined. Finally, the coordinates of this \kD{} centroid are used as the predicted \kD{} embedding for the new \pD{} data point. . -->

<!-- We define the function $z: \mathbb{R}^{n\times p} \rightarrow \mathbb{R}^{m\times p}$, -->

<!-- For the $i^{th}$ point, $z(i) = \arg\min_{j = 1, \dots, b} \sqrt{\sum_{v=1}^{P}(x_{iv} - C^{(2)}_{jv})^2}$, and assign it to $H_h = \{i| z(i) = h\}$. Then, the fitted values for $i$ are defined as $C_{h}^{(2)} = (c_{h1}, c_{h2})$.  -->

The fitted values refers to the \pD{} mappings of the \kD{} model.

>>>>

The fitted values of the points in $H_h$ refers to the \pD{} mapping $C_{h}^{(p)}$ of the corresponding \kD{} model point $C_{h}^{(2)}$.
